comgen-outline

### 2017-07-03 paper/comgen-paper.Rmd
small edits to predictive habituals expts

## Experiment 2b: Endorsing generalizations about events

@@

This is particularly

@@

## Experiment 3: Communicating predictive propensities

In Experiment 2b, we supplied participants with a statement about how often a person has done the action in the past and asked them to judge the correspoding habitual statement.
This raises an interesting question: Does the propensity communicated by a generalization indicate an objective, past frequency or a subjective, future expectation?

@@

In this pair of experiments, we address this by introducing causal events that enable or prevent future actions (e.g., buying a pack of cigarettes; developing an allergy).
In Expt. 3a, we measure *predictive frequency* both when past frequency alone is observed and when these causal factors are introduced.
In Expt. 3b, we examine felicity judgments of the habitual sentence (e.g., \emph{John smokes cigarettes.}; \emph{Susan eats peanut butter.}) in the presence of these causal modifiers.
This allows us to test whether habituals are best explained by a speaker $S_1$ who communicates the objective past frequency or the subjective future frequency.

### Experiment 3a: Prediction elicitation

@@

@@

Only twenty-one of the original thirty-one items were used in order to shorten the experiment.
To increase expected variability, participants saw only the frequencies that led to most intermediate endorsement of the habitual in Expt. 2b. 
In addition, we did not include separate trials for both male and female names for the select items we did in Expt. 2b, since we saw no differences in their endorsements of the habitual.

@@

### Experiment 3b: Felicity judgments

@@

Habitual language conveys generalizations about events and our model decides if a habitual sentence is a pragmatically useful way to describe the rate at which a person does an action, taking into account the listener’s prior beliefs about the action (measured in Expt. 2a). 
We have seen that our computational model endorses statements that communicate generalizations about events with the same sensitivity to context that people exhibit (Expt. 2b).
In Experiment 2b, we varied the type of event and the past frequency with which the person did the action, and found substantial graded variability in the endorsement judgments of people.
<!-- Naive baseline models could not explain these endorsements judgments and our communicative model provided the most parsimonious account of the data in comparison to non-Bayesian models.  -->
<!-- In Experiment 3, we looked at interpretations of habitual statements about different events and again found substantial gradedness that our theory provided the most parsimonious account of. -->
<!-- The theory defines a pair of interpretation and endorsement models and these models can simultaneously account for both data sets. -->
In Experiment 3, we further investigated the nature of the underlying “propensity” scale by introducing enabling and disabling causal evidence, measuring the predicted future frequency (Expt. 3a) and using that, with the model, to predict the felicity of habitual sentences (Expt. 3b). 
To our knowledge, the experiments presented here are first empirical investigations into the truth conditions of habitual sentences and the first test of a formal psychological model of generalizations in language.
In these experiments, we directly manipulated the frequency that the speaker was trying to communicate while measuring the propensity priors.
Thus, it is still possible that the propensity priors that are central to our communicative theory of generalizations are somehow epiphenomenal, correlational associated with generic endorsement but not directly causally related.
In our final case study, we extend our theory to communicating generlizations about causes, and test experimentally whether the propensity prior is indeed causally related to generic endorsement.

>>>>

## Experiment 2b: Endorsing habitual statements

@@

In Experiment 2b, we supplied participants with a statement about how often a person has done the action in the past and asked them to judge the correspoding habitual statement.
This raises an interesting question: Does the propensity communicated by a generalization indicate an objective, past frequency or a subjective, future expectation?
Across two follow-up experiments (Expts. 2c \& 2d), we address this question by manipulating and measuring *predictive frequency* (Expt. 2c) and habitual endorsement (Expt. 2d).

@@

## Experiment 2c: Measuring predictive frequency

@@

In the following pair of experiments, we address this by introducing causal events that enable or prevent future actions (e.g., buying a pack of cigarettes; developing an allergy).
In Expt. 2c, we measure *predictive frequency* both when past frequency alone is observed and when these causal factors are introduced.
In Expt. 2d, we examine endorsements of the habitual sentence (e.g., \emph{John smokes cigarettes.}; \emph{Susan eats peanut butter.}) in the presence of these causal modifiers.
This allows us to test whether habituals are best explained by a speaker $S_1$ who communicates the objective past frequency or the subjective future frequency.

@@

### Methods

@@

Only twenty-one of the original thirty-one items were used in order to shorten the experiment.
To increase expected variability, participants saw only the frequencies that led to the most intermediate endorsement of the habitual in Expt. 2b. 
In addition, we did not include separate trials for both male and female names for the select items we did in Expt. 2b, since we saw no differences in their endorsements of the habitual.

@@

## Experiment 2d: Endorsing habituals under predictive-manipulated conditions

@@

Habitual language conveys generalizations about events and our model decides if a habitual sentence is a pragmatically useful way to describe the rate at which a person does an action, taking into account the listener’s prior beliefs about the action (measured in Expt. 2a). 
We have seen that our computational model endorses statements that communicate generalizations about events with the same sensitivity to context that people exhibit (Expt. 2b).
In Experiment 2b, we varied the type of event and the past frequency with which the person did the action, and found substantial graded variability in the endorsement judgments of people.
<!-- Naive baseline models could not explain these endorsements judgments and our communicative model provided the most parsimonious account of the data in comparison to non-Bayesian models.  -->
<!-- In Experiment 3, we looked at interpretations of habitual statements about different events and again found substantial gradedness that our theory provided the most parsimonious account of. -->
<!-- The theory defines a pair of interpretation and endorsement models and these models can simultaneously account for both data sets. -->
In Experiments 2c \& 2d, we further investigated the nature of the underlying “propensity” scale by introducing enabling and disabling causal evidence, measuring the predicted future frequency (Expt. 2c) and using that, with the model, to predict the felicity of habitual sentences (Expt. 2c). 
To our knowledge, the experiments presented here are first empirical investigations into the truth conditions of habitual sentences and the first test of a formal psychological model of generalizations in language.
In these experiments, we directly manipulated the frequency that the speaker was trying to communicate while measuring the propensity priors.
Thus, it is still possible that the propensity priors that are central to our communicative theory of generalizations are somehow epiphenomenal, correlational associated with generic endorsement but not directly causally related.
In our final case study, we extend our theory to communicating generlizations about causes, and test experimentally whether the propensity prior is indeed causally related to generic endorsement.
